\documentclass{beamer}
\usepackage{multicol,hyperref}
\renewcommand{\arraystretch}{1.5}
\newcommand{\fttheory}[1]{\fcolorbox{blue}{blue}{\color{white}\textbf{#1}\hspace{\textwidth}}}
\newcommand{\ftexampl}[1]{\fcolorbox{orange}{orange}{\color{black}\textbf{#1}\hspace{\textwidth}}}
\newcommand{\ftdata}[1]{\fcolorbox{violet}{violet}{\color{white}\textbf{#1}\hspace{\textwidth}}}
\newcommand{\ftheader}[1]{\fcolorbox{lightgray}{lightgray}{\color{black}\textbf{#1}\hspace{\textwidth}}}
\begin{document}

\begin{frame}{\ftheader{Arbitrage Pricing Theory}}
	\begin{itemize}
		\item \textit{Arbitrage} is the act of costlessly exploiting mispricing of two or more securities to achieve either 1) non-negative profits with certainty or 2) positive profits on average.
		\item Earlier in the course, we studied arbitrage in the context of risk-free bonds.
		\item In this lecture, we are going to study arbitrage in the context of \textit{risky} securities such as stocks, and in so doing, develop the \textit{Arbitrage Pricing Theory} (APT). 
	\end{itemize}
\end{frame}

\begin{frame}{\fttheory{Arbitrage Pricing Theory: Long}}
	Consider a stock that returns
	\begin{equation}
		r_{S}=r_{F}+\alpha+\beta(r_{M}-r_{F})+\epsilon
	\end{equation}
	Importantly, suppose that $\alpha>0$ (the stock is \underline{under}valued). 
	\begin{center}
		\begin{tabular}{l|c|c}
			Security & Cash Flow at $t=0$ & Cash Flow at $t=1$ \\ \hline
			Stock & $-1$ & $(1+r_{S})$ \\
			Market Portfolio & $\beta$ & $-\beta(1+r_{M})$ \\
			Risk-Free Security & $1-\beta$ & $-(1+r_{F})(1-\beta)$\\ \hline
			Arbitrage Portfolio & $0$ & $\alpha+\epsilon$\\
		\end{tabular}
	\end{center}
	Here, we have a portfolio that pays $E[\alpha+\epsilon]=\alpha>0$ on average and costs nothing to setup. 
\end{frame}

\begin{frame}{\ftexampl{Example: Long}}
	Walmart has a beta of $.3659$ and an alpha of $.5450\%$.
	\begin{center}
		\begin{tabular}{ll}
			\multicolumn{2}{l}{Date $t=0$} \\ \hline
			1. & Short .3659 USD worth of market.\\
			2. & Borrow .6341 USD.\\
			3. & Use your 1 USD to buy 1 USD worth of Walmart. \\ \hline
			\multicolumn{2}{l}{Date $t=1$} \\ \hline
			1. & Sell Walmart. \\
			2. & Repay the loan. \\
			3. & Cover your short. \\ \hline
			\multicolumn{2}{l}{You should earn .5450 USD on average.}
		\end{tabular}
	\end{center}
\end{frame}

\begin{frame}{\fttheory{Arbitrage Pricing Theory: Short}}
	Same setup as before...
	\begin{equation}
		r_{S}=r_{F}+\alpha+\beta(r_{M}-r_{F})+\epsilon
	\end{equation}
	...but now suppose that $\alpha<0$ (the stock is \underline{over}valued). 
	\begin{center}
		\begin{tabular}{l|c|c}
			Security & Cash Flow at $t=0$ & Cash Flow at $t=1$ \\ \hline
			Stock & $1$ & $-(1+r_{S})$ \\
			Market Portfolio & $-\beta$ & $\beta(1+r_{M})$ \\
			Risk-Free Security & $\beta-1$ & $(1+r_{F})(1-\beta)$\\ \hline
			Arbitrage Portfolio & $0$ & $-\alpha+\epsilon$\\
		\end{tabular}
	\end{center}
	We have a portfolio that pays $E[-\alpha+\epsilon]=-\alpha>0$ on average and costs nothing to setup. 
\end{frame}

\begin{frame}{\ftexampl{Example: Short}}
	Walgreen's has a beta of $1.0733$ and an alpha of $-.3471\%$.
	\begin{center}
		\begin{tabular}{ll}
			\multicolumn{2}{l}{Date $t=0$} \\ \hline
			1. & Short 1 USD worth of Walgreen's. \\
			2. & Borrow .0733 USD. \\
			3. & Use your 1.0733 USD to buy 1.0733 USD worth of market. \\ \hline
			\multicolumn{2}{l}{Date $t=1$} \\ \hline
			1. & Sell the market. \\
			2. & Repay the loan. \\
			3. & Cover your short. \\ \hline
			\multicolumn{2}{l}{You should earn .3471 USD on average.}
		\end{tabular}
	\end{center}
\end{frame}

\begin{frame}{\fttheory{The Arbitrage Pricing Theory}}
	\begin{itemize}
		\item These examples show that if $\alpha\neq0$, then one can costlessly construct a portfolio that pays $|\alpha|$ on average. 
		\item Suppose, for concreteness, that $\alpha>0$ (as in the Walmart example). Then arbitrageurs start buying the stock. 
		\item According to the laws of supply and demand, the price will rise (the return will fall) until $\alpha=0$.
		\item The APT claims that $\alpha=0$ on average:
			\begin{equation}
				\text{E}[r_{S}-r_{F}]=\beta\text{E}[r_{M}-r_{F}]
			\end{equation}
			which is exactly what the CAPM claims. 
		\item The APT tells us \textit{why} the CAPM should hold and \textit{how} to profit when it breaks.
		\item Note that these trades involve idiosyncratic risk ($\epsilon$) but \underline{not} systematic risk ($r_{M}$)
	\end{itemize}
\end{frame}

\begin{frame}{\fttheory{Multifactor Models}}

	\begin{itemize}
		\item A multifactor model decomposes a security's return into \textit{factors} $f_{1},f_{2},\ldots,f_{N}$:
			\begin{equation}\small
				r_{S}-r_{F}=\alpha+\beta_{1}f_{1}+\beta_{2}f_{2}+\cdots+\beta_{N}f_{N}+\epsilon
			\end{equation}
		\item The CAPM is a 1-factor model with $f_{1}=r_{M}-r_{F}$. 
		\item There are multifactor models for stocks (which we will explore in a moment), bonds, currencies, housing, and other securities. 
		\item In currencies, for example, the two most popular popular factors are ``value'' and ``carry'', each corresponding to the return on a certain portfolio of currencies. 
		\item Again, the APT claims that $\alpha=0$ on average:
			\begin{equation}
				\text{E}[r_{S}-r_{F}]=\beta_{1}\text{E}[f_{1}]+\beta_{2}\text{E}[f_{2}]+\cdots+\beta_{N}\text{E}[f_{N}]
			\end{equation}
	\end{itemize}
\end{frame}

\begin{frame}{\ftdata{Application: Fama-French 3-Factor Model}}
	\begin{itemize}
		\item The Fama-French model is a  multifactor model for stocks. 
		\item It has factors $f_{1}=r_{\text{MKT}}-r_{F}$, $f_{2}=r_{\text{SMB}}$, and $f_{3}=r_{\text{HML}}$.
		\item SMB is a portfolio that goes long (S)mall stocks and short (or (M)inus) (B)ig stocks (as measured by market cap).
		\item Smaller firms outperform bigger firms (3.06\% 1927-2019). 
		\item HML is a portfolio that goes long (H)igh book-to-market stocks and short (or (M)inus) (L)ow book-to-market stocks. 
		\item Two definitions: \textit{value stocks} are stocks with a (H)igh book-to-market ratio, while \textit{growth stocks} are stocks with a (L)ow book-to-market ratio.  
		\item Value stocks outperform growth stocks (4.48\% 1927-2019).
		\item The idea is that smaller stocks and stocks with higher book-to-market are riskier and therefore offer higher returns
		\item \url{https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html}
	\end{itemize}
\end{frame}

\end{document}
